Open archaeology, open source?

### 2023-09-20 analysis/_06-network.qmd
Fix errors and rerender manuscript

oarch_graph <- bind_rows(
  oarch_graph |>
    unnest(gh_commits) |>
    drop_na(author) |> # Apparently real commits, but we can't connect them
    group_by(repo, author) |>
    summarise(category = first(category), tags = first(tags),
              contrib = "commit", n_contrib = n(), .groups = "drop"),
  oarch_graph |>
    unnest(gh_comments) |>
    drop_na(author) |> # Repos with no comments
    group_by(repo, author) |>
    summarise(category = first(category), tags = first(tags),
              contrib = "comment", n_contrib = n(), .groups = "drop"),
  oarch_graph |>
    unnest(gh_issues) |>
    drop_na(author) |> # Repos with no issues
    group_by(repo, author) |>
    summarise(category = first(category), tags = first(tags),
              contrib = "issue", n_contrib = n(), .groups = "drop")
)

@@

```{r extract-graph-repo-repo}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph,category,tags),
                                   edges_common_users(oarch_graph),
                                   directed = FALSE)

@@

```{r fig-graph-repo-repo, eval=FALSE}
iplot <- oarch_graph_repo_repo |>
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = n)) +
  #geom_node_point(aes(colour = group)) +
  #geom_node_text(aes(label = group)) +
  geom_point_interactive(aes(x, y, colour = group, tooltip = repo)) + 
  scale_edge_alpha(trans = "log") +
  labs(edge_alpha = "Common contributors")

@@

oarch_graph_user_user |>
  mutate(degree = centrality_degree()) |>
  filter(degree > 1) |>
  mutate(
    centrality = centrality_betweenness(weights = n),
    group = as.character(group_edge_betweenness())
  ) ->
  oarch_graph_user_user
```

@@

```{r fig-graph-user-user-centrality, eval=TRUE}
oarch_graph_user_user |> 
  ggraph(layout = "graphopt") +
  # geom_edge_link(aes(alpha = n)) +
  geom_edge_arc(alpha = 0.05) +
  geom_node_point(aes(size = centrality), 
                  shape = 21, colour = "#000000", fill = "#ffffff") +
  # scale_edge_alpha(trans = "log") +
  # labs(edge_alpha = "Common repositories") +
  theme_graph()
```

>>>>

oarch_graph <- bind_rows(
  oarch_graph |>
    unnest(gh_commits) |>
    drop_na(author) |> # Apparently real commits, but we can't connect them
    group_by(repo, author) |>
    summarise(contrib = "commit", n_contrib = n(), .groups = "drop"),
  oarch_graph |>
    unnest(gh_comments) |>
    drop_na(author) |> # Repos with no comments
    group_by(repo, author) |>
    summarise(contrib = "comment", n_contrib = n(), .groups = "drop"),
  oarch_graph |>
    unnest(gh_issues) |>
    drop_na(author) |> # Repos with no issues
    group_by(repo, author) |>
    summarise(contrib = "issue", n_contrib = n(), .groups = "drop")
)

@@

```{r extract-graph-repo-repo}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph),
                                   edges_common_users(oarch_graph),
                                   directed = FALSE)

@@

```{r fig-graph-repo-repo-interactive, eval=FALSE}
iplot <- oarch_graph_repo_repo |>
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = n)) +
  #geom_node_point(aes(colour = group)) +
  #geom_node_text(aes(label = group)) +
  geom_point_interactive(aes(x, y, colour = group, tooltip = repo)) + 
  scale_edge_alpha(trans = "log") +
  labs(edge_alpha = "Common contributors")

@@

oarch_graph_user_user |>
  mutate(degree = centrality_degree()) |>
  filter(degree > 1) |>
  mutate(centrality = centrality_betweenness(weights = n)) ->
  oarch_graph_user_user
```

@@

```{r fig-graph-user-user-centrality, eval=FALSE}
oarch_graph_user_user |> 
  ggraph(layout = "graphopt") +
  # geom_edge_link(aes(alpha = n)) +
  geom_edge_arc(alpha = 0.05) +
  geom_node_point(aes(size = centrality), 
                  shape = 21, colour = "#000000", fill = "#ffffff") +
  # scale_edge_alpha(trans = "log") +
  # labs(edge_alpha = "Common repositories") +
  theme_graph()
```
